Supplementary Material for Asymmetry paper

### 2020-05-28 Supplementary/Sup_mat.Rmd
All models run
All models have been run and have minimal divergent transitions

priors_plt <- draws_df$Draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  geom_density(
    kernel = "biweight",
    alpha = .3
    )+ 
  facet_wrap(~Dist_type) + 
  theme_bw()
```

@@

## Experiment 3: Reward
```{r load in gambling data, include = F, echo = F, warning = F, cache=T}
# load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri")
# load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri_draws")
load("../Analyses/Experiment_5_Unequal_Reward/scratch/data/model_data")

@@

# run model 
Reward_m1 <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                 data = model_data,
                 family = "beta",
                 chains = 1,
                 iter = 4000,
                 warmup = 2000)

draws_df <- draws_factor(Reward_m1) %>% 
  mutate(prop = boot::inv.logit(estimate))

@@

```{r PltRewardestimates, echo = F, inlude = T, warning = F, fig.asp=.75, fig.cap=""}
# make separate plots for main effects and interactions 
plt_dist <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Dist_Type,
             fill = Dist_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Distance Type"),
         fill = guide_legend(title = "Distance Type")) +
  scale_x_continuous("Normalised Position")

>>>>

priors_plt <- draws_df$Draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(
    kernel = "biweight",
    alpha = .3
  )+ 
  facet_wrap(~Dist_type) + 
  theme_bw()
```

@@

## Experiment 3: Reward
``` {r GamblingPriorsOnly, include = F, echo = F, warning = F, cache = T}
load("../Analyses/Experiment_5_Unequal_Reward/scratch/data/model_data")

@@

Reward_priors <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                     data = model_data,
                     family = "beta",
                     prior = c(set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar:Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,1)",
                                         class = "Intercept")),
                     chains = 1,
                     iter = 10000,
                     warmup = 5000,
                     sample_prior = "only",
                     control = list(adapt_delta = .99, max_treedepth = 15))
```

``` {r RewardPriorsPlt, include = T, echo = F, fig.asp = .45, fig.cap = "test"}
draws_factor(Reward_priors) %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop,
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(alpha = .3,
               kernel = "biweight") +
  scale_x_continuous(expression(Delta)) +
  facet_wrap(~Dist_Type) + 
  theme_bw()
```

```{r RewardModel, include = F, echo = F, warning = F, cache = T}
# run model 
load("../Analyses/Experiment_5_Unequal_Reward/scratch/data/model_data")
Reward_m1 <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                     data = model_data,
                     family = "beta",
                     prior = c(set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar:Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,1)",
                                         class = "Intercept")),
                     chains = 1,
                     iter = 10000,
                     warmup = 5000,
                     control = list(adapt_delta = .99, max_treedepth = 15))

@@

```{r PltRewardestimates, echo = F, inlude = T, warning = F, fig.asp=.75, fig.cap=""}
# get draws 
draws_df <- draws_factor(Reward_m1) %>% 
  mutate(prop = boot::inv.logit(estimate))

# make separate plots for main effects and interactions 
plt_dist <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Dist_Type,
             fill = Dist_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Distance Type"),
         fill = guide_legend(title = "Distance Type")) +
  scale_x_continuous("Normalised Position")
